### 2020-05-13 Report/aws_325ghz_study.tex
updated text correction scheme

\subsection{Noise}
%
The nominal reciever noise temperature, $T_r$ of each band is listed in
Table~\ref{tab:trec}. The noise of data for individual channels is calculated
as
\begin{equation}
  \sigma^i = c \frac{T^i_r+T^i_a}{\sqrt{\Delta\!f^i\Delta t}}
\end{equation}
where $\sigma^i$ is the noise standard deviation of channel $i$, $c$ is a
scaling factor (see below), $T^i_r$ is the reciever noise temperature of the
channel, $T^i_a$ is the antenna temperature of the channel, $\Delta\!f^i$ is
the bandwidth (in terms of IF) of channel and $\Delta t$ is the integration
time.

@@

\section{Cloud correction by a simple scheme}
%
\dots

>>>>

\subsection{Noise}
%
The nominal reciever noise temperature, $T_r$ of each band is listed in
Table~\ref{tab:trec}. The noise of data for individual channels is calculated
as
\begin{equation}
  \sigma^i = c \frac{T^i_r+T^i_a}{\sqrt{\Delta\!f^i\Delta t}}
  \label{eq:noise}
\end{equation}
where $\sigma^i$ is the noise standard deviation of channel $i$, $c$ is a
scaling factor (see below), $T^i_r$ is the reciever noise temperature of the
channel, $T^i_a$ is the antenna temperature of the channel, $\Delta\!f^i$ is
the bandwidth (in terms of IF) of channel and $\Delta t$ is the integration
time.

@@

\section{Cloud correction by a simple scheme}
%

\begin{figure}[!tb]
	\centering
	\includegraphics[height=65mm]{fit_C34_C42}\hspace{5mm}% 
	\caption{Brightness temperature difference of channel-34 from channel-42 plotted against cloud impact in channel-34 (TB allsky - TB cleasky). The black curve represents the line of best fit as a third order polynomial. }
	\label{fig:fit:c34-42}
\end{figure}

\begin{figure}[!th]
	\centering
	\includegraphics[height=85mm]{PDF_corrected_C34_C42}
	\caption{Deviation of channel-34 measurements to noise free clear-sky cases. The various curves represent the measurements before and after correction. The correction according to \cite{rekha2012potential} is also shown. The two curves with label ``after correction'' are for two different values of noise threshold. }
	\label{fig:correction:c34-42}
\end{figure}

In this section, the 325GHz three channel option  is evaluated for ice cloud correction for 183 GHz channels. We predict the clears-sky value for 183GHz channel based on the brightness temperatures of simulated 325GHz channel data. For correction, the channels from the three option 325GHz and 183GHz are matched according to their weighting functions(Figure~\ref{fig:3ch:prel}). From the five  183 GHz and 325 GHz combinations possible, the weighting functions for channel- 34 and channel-42 have the best match, thus we use this combination for the development of the correction scheme.

A simple regression approach is implemented to estimate the clear-sky values from the measurements. From the simulation dataset, 40000 clear-sky and the corresponding all-sky simulations are selected to develop the correction scheme. Without the availability of actual data, an identical simulation dataset but with noise is used mimic the measurements. The noise for individual channels is calculated according to Equation~\ref{eq:noise}. Before deriving any relationship between the different variables, 50\% of the clear-sky simulations are removed from the dataset. This clear-sky removal is to remove any under-representation of cloudy simulations, as discussed in the Validation section. Further, the simulations from channel-34 with cloud impact greater than 25 K are considered as "too cloudy" and are not included in the correction.

Among the various possible combinations of clear-sky and all-sky pairs for channel-34 and channel-43, the brightness temperature (TB)  differences of channels-34 and 42 are found to be reasonably well correlated against the channel-34 cloud impact (TB clear-sky minus all-sky ). Figure ~\ref{fig:fit:c34-42}  shows the scatter plot of the TB channel-34 minus TB channel-42 against the channel-34 cloud impact. The regression between the two variables gives the correction estimate for channel-34 all-sky measurements :
\begin{equation}
correction = tb^{34} + f(tb0^{42}_{as} - tb0^{32}_{cs})   
\end{equation}
where, $ tb^{34}$ are channel-34 measurements, and $tb0^{42}_{as}$ and $tb0^{32}_{cs}$ are channel-42 and channel-34 simulations for all-sky and clear-sky respectively. 
The correction is applied only to cloudy measurements. All cases with cloud impact less than 0.2 K or greater than 25 K are termed as ``clear'' or ``too cloudy''  respectively and are not corrected. Further, all measurements with TB differences between channel-34 and channel-42 greater than a ``noise-index'' are not adjusted. This check is introduced to avoid correction of clear-sky measurements which are falsely classified as cloudy. the ``noise-index'' is defined as a factor the standard deviation of noise for 183GHz.

The error in the predicted measurements is assessed by calculating the deviation to noise-free clear-sky observations. The occurrence frequency of the deviations is shown in Figure~\ref{fig:correction:c34-42}. When all measurements are corrected for cloud impact, the deviations should follow a gaussian distribution with zero mean. However, without any correction, the measurements show a strong cloud impact, which is indicated by the non-zero values to the left of the peak (orange line). Removing measurements with cloud impact greater than 25 K (green line) reduces the cloud impact far left but not in the intermediate region indicating that it effectively removes the ``too cloudy'' measurements. After adjustment, the cloudy impact in the measurements is considerably reduced, though the spread increases. The sensitivity of the algorithm to correctly adjust the cloudy cases is tested through two different values of the noise-index: $1 \sigma$ and $2\sigma$. As evident from the figure, both values gave almost similar results indicating that the algorithm can correctly identify and adjust most of the cloudy measurements.

For completeness, we also include results from the cloud filtering approach described by \cite{rekha2012potential}. In the report, they describe the usability of 229 GHz (channel-4x) to identify the ice clouds, and filter out all measurements with TB difference between channel-32 and channel-4x greater than 4K. The correction approach when applied to channel-34 is also shown in the Figure (brown curve). The performance of cloud filtering by \cite{rekha2012potential} seems comparable with the regression approach described in this report, however they risk rejecting more than 50\% of the clear cases. With the regression approach, only 2-4\% of the total cases are rejected.

\begin{figure}[!tb]
	\centering
	\includegraphics[height=70mm]{PDF_corrected_C32_C41}\hspace{5mm}% 
	\includegraphics[height=70mm]{PDF_corrected_C33_C41}
	\includegraphics[height=70mm]{PDF_corrected_C35_C43}\hspace{5mm}% 
	\includegraphics[height=70mm]{PDF_corrected_C36_C43}
	\caption{Same as for Figure~\ref{fig:correction:c34-42}, but for other possible combinations of 183GHz and 325 GHz. }
	\label{fig:correction:allchannels}
\end{figure}

The regression approach described above is also extended to other four channel combinations and the results are shown in Figure\ref{fig:correction:allchannels}.
